Connecting scene direction to year and writer

### 2017-06-18 connect_year_writer.Rmd
Gender ratio from writers/directors/etc

What kind of joining can I do? Year, genre, gender of writers/etc

```{r, dependson="pronoun_imdb"}

pronoun_imdb %>%
    inner_join(genre, by = "imdb") ## to get genre

pronoun_imdb %>%
    inner_join(gender, by = "imdb") ## to get gender of writers, etc

```

>>>>

## Differences by gender of writer

We can use the odds ratio to find words coming after "she" that are more likely to be used by female writers/directors/etc and those more likely to be used by male writers/directors/etc. Movies can have both, can have multiple writers and so forth, but the following analysis accounts for that.

```{r gender_ratio, dependson="pronoun_imdb", fig.width=7, fig.height=6}
gender_ratio <- pronoun_imdb %>%
    inner_join(gender, by = "imdb") %>% ## to get gender of writers, etc
    filter(word1 == "she",
           str_detect(word2, "[a-z]+"),
           nchar(word2) > 2) %>%
    group_by(word2) %>%
    mutate(total = n_distinct(scriptID)) %>%
    ungroup %>%
    count(gender, word2, total) %>%
    spread(gender, n, fill = 0) %>%
    mutate(female = (female + 1) / sum(female + 1),
           male = (male + 1) / sum(male + 1),
           ratio = female / male,
           logratio = log2(ratio)) %>%
    arrange(desc(logratio))

gender_ratio %>%
    filter(total > 50) %>%
    group_by(logratio < 0) %>%
    top_n(15, abs(logratio)) %>%
    ungroup() %>%
    mutate(word = reorder(word2, logratio)) %>%
    ggplot(aes(word, ratio - 1, color = logratio < 0)) +
    geom_segment(aes(x = word, xend = word,
                     y = 0, yend = ratio - 1), 
                 size = 1.1, alpha = 0.6) +
    geom_point(size = 3.5) +
    coord_flip() +
    labs(x = NULL, 
         y = "Relative use by women / men",
         title = "Words paired with 'she' from writers/directors/etc of different genders",
         subtitle = "From 4000+ films, verbs mentioned 50+ times\nWomen are more likely to portray women who write, fling, remember, wander\nMen are more likely to portray women who respond, emerge, believe, react") +
    scale_color_discrete(name = "", labels = c("More from women", "More from men")) +
    scale_y_continuous(breaks = c(-0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8),
                       labels = c("-60%", "-40%", "-20%", "Same", "+20%", "+40%", "+60%", "+80%"))
```

What are some words after "she" that have about the same likelihood to come from writers/directors/etc who are men and women?

```{r dependson="gender_ratio"}
gender_ratio %>%
    filter(total > 50) %>%
    arrange(abs(logratio))
```

Words like "still", "and", "drives", "tries", "brings", "listens"...
